A Comparison of Optical and Electronic Methods for the Characterization of Plasmon-Supporting Metal Nanoparticle Systems.

### 2018-01-16 paper_fall_2017/general_exam/general_paper.tex
lots of new stuff

\documentclass[12pt, letterpaper, twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{wrapfig}
\doublespacing
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\bibliographystyle{ieeetr}
\title{Magnetic Effects in Metal Nanoparticle Arrays}
\author{Nicholas P. Montoni}
\date{\center{Wednesday, August 16, 2017\\Chemistry Building 339, 9:30 AM}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Interest in the collective magnetic response of arrays of metal nanoparticles, called magnetic oligomers, has exploded in recent years. This is due to the possibility of applying magnetic plasmon resonances to problems such as biological sensing and imaging, electromagnetic cloaking, and information processing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano,Zhang2006,NordHal2011,NordHal2012}. Plasmonic systems exhibiting magnetic properties have been thoroughly characterized on both the single-oligomer scale and the infinite scale, but open questions remain about the properties and usefulness of magnetic oligomers in the size regime between these two limits\cite{Dionne2016,Weick2013,Engheta2017}. Emphasizing this point is a wealth of research focusing on large, multi-oligomer arrays of nanoparticles. In particular, one such work highlights the complexity of these systems and sets the stage for the tunability and usefulness of magnetic plasmon resonances.

The recent work in question focused on describing one-, two-, and six-oligomer systems using both a quasistatic tight-binding model and full-wave simulations. The quasistatic approximation assumes that an object is so small that light and information travel across it infinitely quickly, or at least faster than the lifetime of any relevant physical phenomenon, such as a plasmon resonance. This is important to note because the formulation of the model is therefore fundamentally different from the simulations; the simulations include retardation effects. So it comes as no surprise that the model and the simulations predicted different properties for the two- and six-oligomer systems. The discrepancy occurred in the spectral ordering of the closed-loop magnetic modes: the tight-binding model predicted that the nodeless magnetic mode was higher in energy while simulations predicted that it was lower in energy. This discrepancy is a clear indication that the quasistatic approximation breaks down for magnetic systems and that retardation effects are in fact necessary to proeprly describe them.

When two or more metal nanoparticles (MNPs) are allowed to interact, the collective excitations of their conduction electrons, called electric plasmons, can hybridize to produce new excitations\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Much work has been done to describe magnetic plasmons both in the single oligomer limit\cite{}, where the aggregates are well-described by the quasistatic approximation, and in the infinite limit, where extended systems are well-defined by condensed matter approaches\cite{}. In between these limits, however, there are still open questions about how to think about magnetic plasmons and what models work best\cite{}.

@@

Beyond investigating previous work, the intuition gained from the simple model will be applied to suggest and explore applications and observables of magnetic plasmon oligomers. Specifically, because these aggregates can couple to and enhance the magnetic field of light, and because of their unique radiative properties, magnetic oligomers have applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{}. This paper documents those unique properties and leverages them as a measure of the importance of retardation effects. As a final exercise, two explanations for these properties are proposed in order to gain insight and intuition into the behavior of more complicated MNP aggregates.

>>>>

\documentclass[12pt, letterpaper, twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{wrapfig}
\doublespacing
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\bibliographystyle{ieeetr}
\title{Quantifying the Role of Magnetic Effects in Metal Nanoparticle Arrays}
\author{Nicholas P. Montoni}
\date{\center{Wednesday, August 16, 2017\\Chemistry Building 339, 9:30 AM}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
When two or more metal nanoparticles (MNPs) are allowed to interact, the collective excitations of their conduction electrons, called electric plasmons, can hybridize to produce new excitations\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Much work has been done to describe magnetic plasmons both in the single oligomer limit\cite{Dionne2016}, where the aggregates are well-described by the quasistatic approximation, and in the infinite limit, where extended systems are well-defined by condensed matter approaches\cite{Weick2013}. In between these limits, however, there are still open questions about how to think about magnetic plasmons and what models work best\cite{Engheta2017}.

@@

Beyond investigating previous work, the intuition gained from the simple model will be applied to suggest and explore applications and observables of magnetic plasmon oligomers. Specifically, because these aggregates can couple to and enhance the magnetic field of light, and because of their unique radiative properties, magnetic oligomers have applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}. This paper documents those unique properties and leverages them as a measure of the importance of retardation effects. As a final exercise, two explanations for these properties are proposed in order to gain insight and intuition into the behavior of more complicated MNP aggregates.

### 2018-01-16 paper_nov_2017/doc/latex/achemso/achemso-demo.tex
lots of new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Andrew N. Other}
\altaffiliation{A shared footnote}
\author{Fred T. Secondauthor}
\altaffiliation{Current address: Some other place, Othert\"own,
Germany}
\author{I. Ken Groupleader}
\altaffiliation{A shared footnote}
\email{i.k.groupleader@unknown.uu}
\phone{+123 (0)123 4445556}
\fax{+123 (0)123 4445557}
\affiliation[Unknown University]
{Department of Chemistry, Unknown University, Unknown Town}
\alsoaffiliation[Second University]
{Department of Chemistry, Second University, Nearby Town}
\author{Susanne K. Laborator}
\email{s.k.laborator@bigpharma.co}
\affiliation[BigPharma]
{Lead Discovery, BigPharma, Big Town, USA}
\author{Kay T. Finally}
\affiliation[Unknown University]
{Department of Chemistry, Unknown University, Unknown Town}
\alsoaffiliation[Second University]
{Department of Chemistry, Second University, Nearby Town}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{A Comparison of Optical and Electronic Methods for the Characterization of Plasmon-Supporting Metal Nanoparticle Systems.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{IR,NMR,UV}
\keywords{American Chemical Society, \LaTeX}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.  The document should begin with an
%% abstract, if appropriate.  If one is given and should not be, the
%% contents will be gobbled.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Electron-energy loss spectroscopy (EELS) is an experimentally viable method of nanoscale imaging and probing plasmonic character of metal nanoparticle (MNP) systems. Another well-known technique, cathodoluminescence (CL), also provides information. A similar technique that provides new information, called Electron Energy Gain Spectroscopy (EEGS) is a method that has yet to be studied in full. Here, we present a comparison of the observables gleaned from EELS, CL, EEGS, and optical scattering and absorption simulations on MNP systems.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
This is a paragraph of text to fill the introduction of the
demonstration file.  The demonstration file attempts to show the
modifications of the standard \LaTeX\ macros that are implemented by
the \textsf{achemso} class.  These are mainly concerned with content,
as opposed to appearance.

\section{Results and discussion}

\subsection{Outline}

The document layout should follow the style of the journal concerned.
Where appropriate, sections and subsections should be added in the
normal way. If the class options are set correctly, warnings will be
given if these should not be present.

@@

This will usually read something like: ``Experimental procedures and
characterization data for all new compounds. The class will
automatically add a sentence pointing to the information on-line:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tocentry}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=acnac3,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Masiello}
\email{masiello@chem.washington.edu}
\affiliation[University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA, 98195}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The Effects of Retardation on the Energy Ordering and Tunability of Magnetic Plasmon Resonances]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{LSPR, EELS, MNP}
\keywords{plasmon}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials. Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing. For these reasons, it is imperative to understand the properties of such systems on small and large scales. We show, through theory and simulation, that the energy ordering of the magnetic modes of these systems depends on factors such as size, spacing, and environment in ways that purely electric plasmons do not. We culminate this study with a parametrization of the fully retarded magnetic coupling, providing a route to characterizing extended chains and arrays of magnetic plasmon oligomers.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Intro: rephrase and elaborate on 2016 Nano Letters. Discuss plasmon hybridization theory and incorporating retardation effects. Discussion of issue with twomer, how we plan to solve it. Probably going to put the big, important equation there and discuss iterative method?
\section{Results and discussion}
Moving on to the results to prove that our patch-up of the Hamiltonian works well. Compare twomer, threemer (chain and ring), potentially fourmer to BEM simulation. Will need a couple of good figures, including diagrams.
Discuss parametrization of magnetic coupling. Implement, compare full couplings to only nearest-neighbor couplings - surprise! Nearest neighbor coupling does really, really well.
Finally, explore dielectric background (that cool plot of NN-NS)
Now that we all agree, move on to periodic/infinite systems. Do pretty much the same shit as before, except now you are plotting net magnetization instead of energy eigenvalues. Perhaps find a way to represent spin-spin correlation.

\section{Conclusion}
We have shown that magnetic plasmon oligomers are highly versatile and tunable. We have offered various routes towards using both small and extended arrays of oligomers as optical switches. The anti-/ferromagnetic modes of magnetic plasmon oligomers exhibit a disinct and contrary-to-intuition tendency to switch energy ordering as a function of system scale. Utiliziing this property, arrays of oligomers can be desined to have specific optical properties, and extended chains or arrays can be designed to switch their favored magnetic character on a location-by-location basis. These properties open the doors for specific nanoscale sensing and information transmission.

@@

A listing of the contents of each file supplied as Supporting Information
should be included. For instructions on what should be included in the
Supporting Information as well as how to prepare this material for
publications, refer to the journal's Instructions for Authors.

The following files are available free of charge.
\begin{itemize}
  \item Filename: brief description
  \item Filename: brief description
\end{itemize}

@@
